\documentclass[a5paper]{article}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{geometry}
\geometry{a5paper}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{multicol}
\theoremstyle{definition}
\newtheorem{exmp}{Example}[section]
\newtheorem{theorem}{Theorem}

\setlength{\parindent}{5em}
\setlength{\parskip}{2em}
\begin{document}
\author{
    \textbf{Ibrahim Abou Elenein} 50-17004
  \and
    \textbf{Jack Amir} 50-2421
    \and
    \textbf{Moamen Nazmy} 50-19334
    \and
    \textbf{Somaya} 50-8504
}
\title{\textbf{Literature review Introducion}}
\maketitle
% \tableofcontents
% \section{Introduction}
\subsection{Introduciton}
Chronic low back pain is one of the special challgenes in health care
There is no unique apporach to treart chronic low pack
A vartitey of methods are used to treat chronic low back pain
But the effect of these methods have not been investigated.
\textit{(Hasanpour, Dehghani and Solati (2018)).}

\par

% importance


\noindent
 This is of special importance because recovery for people who develop chronic
 low back pain and disability is increasingly less likely the longer the
 problems persist. [2]


\noindent
% sloutions
Some suggested sloutions are letting the patient to take regular exercise
of pilates or mckenzie, lumbar stabilization or dynamic stretching.

\subsection{Purpose and research question of the literature review}
The purpose of this study is to
examine the effect of pilates and other exercise on chronic low back pain
and how this will affect on the patient’s pain and general health.


\subsection{Operational Definition}

\textbf{Low back pain}
is the feeling low back pain with a history of more than 4 months
without any pathological symptoms.
\textit{(Hasanpour et al. (2018)).}

\noindent
\textbf{Pilates}
Pilates is a method of exercise and movement reeducation
based on interpretations of the work and teachings of Josef Pilates
\textit{Henry Wajswelner, Ben Metcalf , and Kim Bennell (2013)}



\begin{thebibliography}{10}
\bibitem{website}
Koes, B W et al. `Diagnosis and treatment of low back pain.` BMJ (Clinical
research ed.) vol. 333,7555 (2006): 1430-4. doi:10.1136/bmj.332.7555.1430

\end{thebibliography}

\end{document}
