\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{geometry}
\geometry{a4paper}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{multicol}
\theoremstyle{definition}
\newtheorem{exmp}{Example}[section]
\newtheorem{theorem}{Theorem}

\setlength{\parindent}{4em}
\setlength{\parskip}{1em}
\begin{document}
\author{
    \textbf{Ibrahim Abou Elenein} 49-17004
  \and
    \textbf{Jack Amir} 49-2421
    \and
    \textbf{Moamen Nazmy} 49-19334
    \and
    \textbf{Somaya} 49-8504
}
\title{\textbf{Methodology}}
\maketitle
% \tableofcontents
% \section{Introduction}
\subsection{Search engines and delimiters}
The research studies included in the literature review were
obtained using the search engine Medline. The delimiters used included full-text,
reference available, peer reviewed, and Narrow language English.
The years of publication were chosen from 2016 till 2021, which gave 16
results.

\subsection{Irrelvant Primary, Secondary}

 Out of the 16 results, \textbf{seven} results were  secondary sources, and
\textbf{six} studies were primary
but irrelevant to the examined research question.
One Study was irrelevant as testing the incorporation of training related to non
specific low back pain
Another one is because testing the necessary number of weeks to improve non specific low back pain
excluded because it's a protocol (doesn't have results)
The next one is excluded because physical inactivity , low educational levels , more advanced ages are tested
if they are factors affecting low back pain
The next one is excluded because chronic generalized painis not low back pain.
The next one is excluded because neck pain is not low back pain.
\subsection{Primaary Relevant}
The remaining \textbf{three} studeis
\textit{
    (Diaz,C. et al. 2017,
    Hasanpou - Dehkordi et al. 2017, Bhadauria \& Gurudut, 2017).}
were primary relevant to the
examined question so they are included in the literature
\end{document}
